R Notebook

### 2023-11-01 Tensor MSSA.rmd
Minor change

Задача параметров и генерация рядов
```{r}
N <- 23
L <- 12
series.number <- 20
sigma <- 1.5
iterations <- 1000
# set.seed(5)

# rank of the time series
r <- 1
s <- map(1:series.number, function(x) runif(1, 1, 4) * exp(1:N * runif(1, 0.001, 0.07)))
s.hankel <- lapply(s, hankel, L)
mat <- reduce(s.hankel, cbind)
u.svd <- svd(mat)
# signal subspace
true.subspace <- u.svd$u[, 1:min(r, N - L + 1), drop = FALSE]
```

@@

Mean MSE for matrix and tensor approaches:
```{r}
mean(apply(mse.mat, 1, mean))
mean(apply(mse.tens, 1, mean))
mean(apply(mse.mat, 1, mean)) - mean(apply(mse.tens, 1, mean))
```

>>>>

Задача параметров и генерация рядов
```{r}
N <- 23
L <- 12
series.number <- 5
sigma <- 1.5
iterations <- 1000
# set.seed(5)

# rank of the time series
r <- 1
# generating series with ranodm parameters
# s <- map(1:series.number, function(x) runif(1, 1, 4) * exp(1:N * runif(1, 0.001, 0.07)))
# generating series by hand
s <- map(1:series.number, function(x) exp(1:N * x / 1000))
s.hankel <- lapply(s, hankel, L)
mat <- reduce(s.hankel, cbind)
u.svd <- svd(mat)
# signal subspace
true.subspace <- u.svd$u[, 1:min(r, N - L + 1), drop = FALSE]
```

@@

Mean MSE for matrix and tensor approaches:
```{r}
mean(apply(mse.mat, 1, mean))
mean(apply(mse.tens, 1, mean))
mean(apply(mse.mat, 1, mean)) / mean(apply(mse.tens, 1, mean))
# mean(apply(mse.mat, 1, mean)) - mean(apply(mse.tens, 1, mean))
```
